BurgerTown Presents: Open Adcess

### 2017-05-01 ideas.tex
added head on ad
black site, baristas

>>>>

Engineers had no solidarity, so the revolution was carried out by baristas, who poured healing crystals in the coffee of business executives and owners of public and private firms, until the means of production were handed over to the ACM with a bit of attitude but a recognition of the rightness of the action, like a teenager returning the car keys to Mom.

Citizens who write unapproved symbols on the punishment blackboard are sent to a second black site. And those who write unapproved symbols on \emph{that} blackboard are eliminated because there's a limit to the number of blackboard licensing lawyers a society can employ.
